%-----------------------------------------------------------------------------------------------
\makeatletter
\immediate\write18{datelog > \jobname.info}
\makeatother
%-----------------------------------------------------------------------------------------------
% Journal information
\JournalInfo{engrXiv}
\Archive{Compiled on \input{\jobname.info} -- Version \input{00-00-PreprintVersion.tex}}
% Article title
\PaperTitle{On Polyekthetic Processes}
\Authors{%
    C.~Naaktgeboren\textsuperscript{1$\star$},
}
\affiliation{%
    \textsuperscript{1}%
    \textit{%
        Adjunct Professor.
        Universidade Tecnológica Federal do Paraná -- UTFPR, Câmpus Guarapuava.
        Grupo de Pesquisa em Ciências Térmicas.
}}
\affiliation{%
    \textsuperscript{$\star$}%
    \textbf{Corresponding  author}: NaaktgeborenC$\cdot$PhD@gmail$\cdot$com
}
\Keywords{%
    Thermodynamics ---
    Polyekthetic Processes ---
    Polyekthetic Exponent ---
    Bridgman's Relations ---
    Polytropic Processes
}
\newcommand{\keywordname}{Keywords}
\Highlights{%
    Proposes `polyekthetic' process: a generalization of polytropic processes ---
    Proposes constant-arbitrary property process polyekthetic exponents $k_{ij\ell}$ ---
    Gives general solution for $k_{ij\ell}$ ---
    Provides examples and discussions.
}
\newcommand{\highlightname}{Highlights}
%-----------------------------------------------------------------------------------------------
\Abstract{%
    This Preprint introduces  \emph{polyekthetic}  processes,  a  generalization  of  polytropic
    processes.  The  etymology  of  the  new  term  is  given,  and  the  concept  is  explained
    theoretically. A useful associated definition for constant-property processes, for arbitrary
    properties  and  expressions  thereof,  is  given,  and  associated  polyekthetic  exponents
    $k_{ij\ell}$ are defined and a general solution  is  obtained.  Examples  on  van-der-Waals,
    general, and ideal gas substances are provided with discussions.
}
%-----------------------------------------------------------------------------------------------
